Neural dialogue act tagging with transformer pre-training (or something like that...)

### 2019-04-05 abstract.tex
upd

  Pre-trained models benefit from learning on large amounts of online data, however it might be the case that for dialogue act tagging additional information only present in natural dialogue data will be useful. Therefore, we evaluate the impact of disfluencies and non-verbal signals, such as laughters on the performance of our models. For the datasets where no annotation for disfluencies is available, this information can be predicted from recognised speech \citep{hough2017joint,shalyminov2018multi}.

  PoS tags

>>>>

  Pre-trained models benefit from learning on large amounts of online data, however it might be the case that for dialogue act tagging additional information only present in natural dialogue data will be useful. Therefore, we evaluate the impact of disfluencies and non-verbal signals, such as laughters on the performance of our models. \textbf{(How?)} For the datasets where no annotation for disfluencies is available, this information can be predicted from recognised speech \citep{hough2017joint,shalyminov2018multi}.

  Furthermore PoS tags
